Codebook created on 2025-06-19 at 2025-06-19 09:49:51

### 2025-06-19 codebook_data.Rmd
closed data with open questions

---
title: "Codebook created on 2025-05-21 at 2025-05-21 15:18:06"
output: github_document
---

@@

## Dataset description
The data contains 634 cases and 28 variables.

>>>>

---
title: "Codebook created on 2025-06-19 at 2025-06-19 09:49:51"
output: github_document
---

@@

## Dataset description
The data contains 633 cases and 29 variables.
